---
title: "The impacts of pesticide exposure on fish conspecific behavioural interactions: systematic review and meta-analysis - data extraction"
author: "Kyle Morrison"
date: "2023-11-23"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
pacman::p_load(tidyverse,
              here,
              shinyDigitise,
              metaDigitise)
```


# **Shinydigitise and Metadigitise** 
```{r}
shinyDigitise(dir = "C:/Users/khtmo/OneDrive - UNSW/University/PhD_Chapters/4_fish_soc_ma/fish_conspecific_behaviour_MA/data_extraction/data_extraction_figures")


metaD <- metaDigitise(dir = "C:/Users/khtmo/OneDrive - UNSW/University/PhD_Chapters/4_fish_soc_ma/fish_conspecific_behaviour_MA/data_extraction/data_extraction_figures")

MetaD

write.csv(metaD,file="fish_soc_ma_shinydigitise.csv")

```

# **Calculate median shoal size for each species** 
```{r}
dataset_collective_behaviour <- read_csv(here("data", "fish_conspecific_behaviour_ma_data_pre_check.csv"))

dataset_collective_behaviour <- dataset_collective_behaviour %>% 
  filter(behaviour_measured_standardised == "collective behaviour") %>% 
  select(c(study_id, species_english, behavioural_assay_standardised, control_shoal_n, treatment_shoal_n, control_fish_n, treatment_fish_n)) %>% 
    mutate(control_shoal_n = as.numeric(control_shoal_n),
    treatment_shoal_n = as.numeric(treatment_shoal_n)
  )

median_shoal_sample_size_per_species <- dataset_collective_behaviour %>%
mutate(control_shoal_size = control_fish_n / control_shoal_n,
         treatment_shoal_size = treatment_fish_n / treatment_shoal_n) %>% 
  group_by(species_english) %>%
  summarise(median_control_shoal_n = median(control_shoal_size, na.rm = TRUE),
    median_treatment_shoal_n = median(treatment_shoal_size, na.rm = TRUE)
  )

```

# **Faria et al., 2021**
DOI: 10.1016/j.envint.2020.106253
Figure1ca extraction
```{r}
faria_2021_1ca <- read_csv(here("data_extraction", "data_extraction_figures", "faria_2021_fig1ca_raw.csv"))

# Calculate mean for each variable in Group
faria_2021_1ca_mean <- tapply(faria_2021_1ca$average_interfish_distance, faria_2021_1ca$group, mean, na.rm = TRUE)

# Calculate standard deviation for each variable in Group
faria_2021_1ca_sd <- tapply(faria_2021_1ca$average_interfish_distance, faria_2021_1ca$group, sd, na.rm = TRUE)

# Define a function to calculate SE
calculate_se <- function(x) {
  sqrt(var(x, na.rm = TRUE) / length(x))
}

# Calculate standard error for each variable in group
faria_2021_1ca_se <- tapply(faria_2021_1ca$average_interfish_distance, faria_2021_1ca$group, function(x) calculate_se(x) / sqrt(length(x)))

faria_2021_1ca_sample_size <- tapply(faria_2021_1ca$average_interfish_distance, faria_2021_1ca$group, length)

# Combine the results into a data frame
faria_2021_1ca_processed <- data.frame(Group= names(faria_2021_1ca_mean),
                                       Mean = faria_2021_1ca_mean,
                             SD = faria_2021_1ca_sd,
                             SE = faria_2021_1ca_se,
                             Sample = faria_2021_1ca_sample_size)

# write.csv(faria_2021_1ca_processed, file.path(here("data_extraction", "data_extraction_figures"), "faria_2021_1ca_processed.csv"), row.names = FALSE)

```

Figure1ca extraction
```{r}
faria_2021_1cb <- read_csv(here("data_extraction", "data_extraction_figures", "faria_2021_fig1cb_raw.csv"))

# Calculate mean for each variable in Group
faria_2021_1cb_mean <- tapply(faria_2021_1cb$farthest_distance, faria_2021_1cb$group, mean, na.rm = TRUE)

# Calculate standard deviation for each variable in Group
faria_2021_1cb_sd <- tapply(faria_2021_1cb$farthest_distance, faria_2021_1cb$group, sd, na.rm = TRUE)

# Calculate standard error for each variable in group
faria_2021_1cb_se <- tapply(faria_2021_1cb$farthest_distance, faria_2021_1cb$group, function(x) calculate_se(x) / sqrt(length(x)))

faria_2021_1cb_sample_size <- tapply(faria_2021_1cb$farthest_distance, faria_2021_1cb$group, length)

# Combine the results into a data frame
faria_2021_1cb_processed <- data.frame(Group= names(faria_2021_1cb_mean),
                                       Mean = faria_2021_1cb_mean,
                                       SD = faria_2021_1cb_sd,
                                       SE = faria_2021_1cb_se,
                                       Sample = faria_2021_1cb_sample_size)

# write.csv(faria_2021_1cb_processed, file.path(here("data_extraction", "data_extraction_figures"), "faria_2021_1cb_processed.csv"), row.names = FALSE)

```

Collective behaviour figures
```{r}
faria_2021_collective_behaviour_raw <- read_csv(here("data_extraction", "data_extraction_figures", "faria_2021_collective_behaviour_raw.csv"))

faria_2021_collective_behaviour_raw_processed <- faria_2021_collective_behaviour_raw %>% 
  mutate(mean_n = n_fish / n_shoal,
         design_effect = 1 + (mean_n - 1) * 0.5,
         n_effective = n_fish / design_effect,
         sd_shoal = se * sqrt(n_shoal),
         sd_fish = se * sqrt(n_fish))

# write.csv(faria_2021_collective_behaviour_raw_processed, file.path(here("data_extraction", "data_extraction_figures"), "faria_2021_collective_behaviour_raw_processed.csv"), row.names = FALSE)

```

# **Hawkey et al., 2020**
DOI: 10.1016/j.ntt.2019.106853
Collective behaviour figures
```{r}
hawkey_2020_collective_behaviour_raw <- read.csv(here("data_extraction", "data_extraction_figures", "hawkey_2020_collective_behaviour_raw.csv"))

hawkey_2020_collective_behaviour_processed <- hawkey_2020_collective_behaviour_raw %>% 
 mutate(mean_n = n_fish / n_shoal,
         design_effect = 1 + (mean_n - 1) * 0.5,
         n_effective = n_fish / design_effect,
         sd_shoal = se * sqrt(n_shoal),
         sd_fish = se * sqrt(n_fish))

# write.csv(hawkey_2020_collective_behaviour_processed, file.path(here("data_extraction", "data_extraction_figures"), "hawkey_2020_collective_behaviour_processed.csv"), row.names = FALSE)

```

Collective behaviour figures
```{r}
hawkey_2021_collective_behaviour_raw <- read.csv(here("data_extraction", "data_extraction_figures", "hawkey_2021_collective_behaviour_raw.csv"))

hawkey_2021_collective_behaviour_processed <- hawkey_2021_collective_behaviour_raw %>% 
 mutate(mean_n = n_fish / n_shoal,
         design_effect = 1 + (mean_n - 1) * 0.5,
         n_effective = n_fish / design_effect,
         sd_shoal = se * sqrt(n_shoal),
         sd_fish = se * sqrt(n_fish))

# write.csv(hawkey_2021_collective_behaviour_processed, file.path(here("data_extraction", "data_extraction_figures"), "hawkey_2021_collective_behaviour_processed.csv"), row.names = FALSE)

```

# **Hussian et al., 2020**
DOI:10.3390/ijerph17134632
Figure 6a extraction
```{r}
# Load the CSV file
hussian_2020_fig6a <- read_csv(here("data_extraction", "data_extraction_figures", "hussian_2020_fig6a_raw.csv"))

# Calculate mean for each variable in Group
hussian_2020_fig6a_mean <- tapply(hussian_2020_fig6a$value, hussian_2020_fig6a$group, mean, na.rm = TRUE)

# Calculate standard deviation for each variable in Group
hussian_2020_fig6a_sd <- tapply(hussian_2020_fig6a$value, hussian_2020_fig6a$group, sd, na.rm = TRUE)

# Calculate standard error for each variable in group
hussian_2020_fig6a_se <- tapply(hussian_2020_fig6a$value, hussian_2020_fig6a$group, function(x) sd(x) / sqrt(length(x)))

hussian_2020_fig6a_sample_size <- tapply(hussian_2020_fig6a$value, hussian_2020_fig6a$group, length)

# Combine the results into a data frame
hussian_2020_fig6a_processed <- data.frame(Group= names(hussian_2020_fig6a_mean),
                                           Mean = hussian_2020_fig6a_mean,
                                           SD = hussian_2020_fig6a_sd,
                                           SE = hussian_2020_fig6a_se,
                                           Sample = hussian_2020_fig6a_sample_size)

# write.csv(hussian_2020_fig6a_processed, file.path(here("data_extraction", "data_extraction_figures"), "hussian_2020_fig6a_processed.csv"), row.names = FALSE)


```

Figure 6f extraction
```{r}
# Load the CSV file
hussian_2020_fig6f <- read_csv(here("data_extraction", "data_extraction_figures", "hussian_2020_fig6f_raw.csv"))

# Calculate mean for each variable in Group
hussian_2020_fig6f_mean <- tapply(hussian_2020_fig6f$value, hussian_2020_fig6f$group, mean, na.rm = TRUE)

# Calculate standard deviation for each variable in Group
hussian_2020_fig6f_sd <- tapply(hussian_2020_fig6f$value, hussian_2020_fig6f$group, sd, na.rm = TRUE)

# Calculate standard error for each variable in group
hussian_2020_fig6f_se <- tapply(hussian_2020_fig6f$value, hussian_2020_fig6f$group, function(x) sd(x) / sqrt(length(x)))

hussian_2020_fig6f_sample_size <- tapply(hussian_2020_fig6f$value, hussian_2020_fig6f$group, length)

# Combine the results into a data frame
hussian_2020_fig6f_processed <- data.frame(Group= names(hussian_2020_fig6f_mean),
                                           Mean = hussian_2020_fig6f_mean,
                                           SD = hussian_2020_fig6f_sd,
                                           SE = hussian_2020_fig6f_se,
                                           Sample = hussian_2020_fig6f_sample_size)

# write.csv(hussian_2020_fig6f_processed, file.path(here("data_extraction", "data_extraction_figures"), "hussian_2020_fig6f_processed.csv"), row.names = FALSE)

```

Figure 8a extraction
```{r}
# Load the CSV file
hussian_2020_fig8a <- read_csv(here("data_extraction", "data_extraction_figures", "hussian_2020_fig8a_raw.csv"))

# Calculate mean for each variable in Group
hussian_2020_fig8a_mean <- tapply(hussian_2020_fig8a$value, hussian_2020_fig8a$group, mean, na.rm = TRUE)

# Calculate standard deviation for each variable in Group
hussian_2020_fig8a_sd <- tapply(hussian_2020_fig8a$value, hussian_2020_fig8a$group, sd, na.rm = TRUE)

# Calculate standard error for each variable in group
hussian_2020_fig8a_se <- tapply(hussian_2020_fig8a$value, hussian_2020_fig8a$group, function(x) sd(x) / sqrt(length(x)))

hussian_2020_fig8a_sample_size <- tapply(hussian_2020_fig8a$value, hussian_2020_fig8a$group, length)

# Combine the results into a data frame
hussian_2020_fig8a_processed <- data.frame(Group= names(hussian_2020_fig8a_mean),
                                           Mean = hussian_2020_fig8a_mean,
                                           SD = hussian_2020_fig8a_sd,
                                           SE = hussian_2020_fig8a_se,
                                           Sample = hussian_2020_fig8a_sample_size)

# write.csv(hussian_2020_fig8a_processed, file.path(here("data_extraction", "data_extraction_figures"), "hussian_2020_fig8a_processed.csv"), row.names = FALSE)

```

Figure 8b extraction
```{r}
# Load the CSV file and remove the unnecessary column
hussian_2020_fig8b <- read_csv(here("data_extraction", "data_extraction_figures", "hussian_2020_fig8b_raw.csv"))

# Calculate mean for each variable in Group
hussian_2020_fig8b_mean <- tapply(hussian_2020_fig8b$value, hussian_2020_fig8b$group, mean, na.rm = TRUE)

# Calculate standard deviation for each variable in Group
hussian_2020_fig8b_sd <- tapply(hussian_2020_fig8b$value, hussian_2020_fig8b$group, sd, na.rm = TRUE)

# Calculate standard error for each variable in group
hussian_2020_fig8b_se <- tapply(hussian_2020_fig8b$value, hussian_2020_fig8b$group, function(x) sd(x) / sqrt(length(x)))

hussian_2020_fig8b_sample_size <- tapply(hussian_2020_fig8b$value, hussian_2020_fig8b$group, length)

# Combine the results into a data frame
hussian_2020_fig8b_processed <- data.frame(Group= names(hussian_2020_fig8b_mean),
                                           Mean = hussian_2020_fig8b_mean,
                                           SD = hussian_2020_fig8b_sd,
                                           SE = hussian_2020_fig8b_se,
                                           Sample = hussian_2020_fig8b_sample_size)

# write.csv(hussian_2020_fig8b_processed, file.path(here("data_extraction", "data_extraction_figures"), "hussian_2020_fig8b_processed.csv"), row.names = FALSE)

```

Figure 8c extraction
```{r}
# Load the CSV file and remove the unnecessary column
hussian_2020_fig8c <- read_csv(here("data_extraction", "data_extraction_figures", "hussian_2020_fig8c_raw.csv"))

# Calculate mean for each variable in Group
hussian_2020_fig8c_mean <- tapply(hussian_2020_fig8c$value, hussian_2020_fig8c$group, mean, na.rm = TRUE)

# Calculate standard deviation for each variable in Group
hussian_2020_fig8c_sd <- tapply(hussian_2020_fig8c$value, hussian_2020_fig8c$group, sd, na.rm = TRUE)

# Calculate standard error for each variable in group
hussian_2020_fig8c_se <- tapply(hussian_2020_fig8c$value, hussian_2020_fig8c$group, function(x) sd(x) / sqrt(length(x)))

hussian_2020_fig8c_sample_size <- tapply(hussian_2020_fig8c$value, hussian_2020_fig8c$group, length)

# Combine the results into a data frame
hussian_2020_fig8c_processed <- data.frame(Group= names(hussian_2020_fig8c_mean),
                                           Mean = hussian_2020_fig8c_mean,
                                           SD = hussian_2020_fig8c_sd,
                                           SE = hussian_2020_fig8c_se,
                                           Sample = hussian_2020_fig8c_sample_size)

# write.csv(hussian_2020_fig8c_processed, file.path(here("data_extraction", "data_extraction_figures"), "hussian_2020_fig8c_processed.csv"), row.names = FALSE)

```

Figure 9a extraction
```{r}
# Load the CSV file
hussian_2020_fig9a <- read_csv(here("data_extraction", "data_extraction_figures", "hussian_2020_fig9a_raw.csv"))

# Calculate mean for each variable in Group
hussian_2020_fig9a_mean <- tapply(hussian_2020_fig9a$value, hussian_2020_fig9a$group, mean, na.rm = TRUE)

# Calculate standard deviation for each variable in Group
hussian_2020_fig9a_sd <- tapply(hussian_2020_fig9a$value, hussian_2020_fig9a$group, sd, na.rm = TRUE)

# Calculate standard error for each variable in group
hussian_2020_fig9a_se <- tapply(hussian_2020_fig9a$value, hussian_2020_fig9a$group, function(x) sd(x) / sqrt(length(x)))

hussian_2020_fig9a_sample_size <- tapply(hussian_2020_fig9a$value, hussian_2020_fig9a$group, length)

# Combine the results into a data frame
hussian_2020_fig9a_processed <- data.frame(Group= names(hussian_2020_fig9a_mean),
                                           Mean = hussian_2020_fig9a_mean,
                                           SD = hussian_2020_fig9a_sd,
                                           SE = hussian_2020_fig9a_se,
                                           Sample = hussian_2020_fig9a_sample_size)

# write.csv(hussian_2020_fig9a_processed, file.path(here("data_extraction", "data_extraction_figures"), "hussian_2020_fig9a_processed.csv"), row.names = FALSE)

```

Figure 9b extraction
```{r}
# Load the CSV file
hussian_2020_fig9b <- read_csv(here("data_extraction", "data_extraction_figures", "hussian_2020_fig9b_raw.csv"))

# Calculate mean for each variable in Group
hussian_2020_fig9b_mean <- tapply(hussian_2020_fig9b$value, hussian_2020_fig9b$group, mean, na.rm = TRUE)

# Calculate standard deviation for each variable in Group
hussian_2020_fig9b_sd <- tapply(hussian_2020_fig9b$value, hussian_2020_fig9b$group, sd, na.rm = TRUE)

# Calculate standard error for each variable in group
hussian_2020_fig9b_se <- tapply(hussian_2020_fig9b$value, hussian_2020_fig9b$group, function(x) sd(x) / sqrt(length(x)))

hussian_2020_fig9b_sample_size <- tapply(hussian_2020_fig9b$value, hussian_2020_fig9b$group, length)

# Combine the results into a data frame
hussian_2020_fig9b_processed <- data.frame(Group= names(hussian_2020_fig9b_mean),
                                           Mean = hussian_2020_fig9b_mean,
                                           SD = hussian_2020_fig9b_sd,
                                           SE = hussian_2020_fig9b_se,
                                           Sample = hussian_2020_fig9b_sample_size)

# write.csv(hussian_2020_fig9b_processed, file.path(here("data_extraction", "data_extraction_figures"), "hussian_2020_fig9b_processed.csv"), row.names = FALSE)

```

Figure 9c extraction
```{r}
# Load the CSV file
hussian_2020_fig9c <- read_csv(here("data_extraction", "data_extraction_figures", "hussian_2020_fig9c_raw.csv"))

# Calculate mean for each variable in Group
hussian_2020_fig9c_mean <- tapply(hussian_2020_fig9c$value, hussian_2020_fig9c$group, mean, na.rm = TRUE)

# Calculate standard deviation for each variable in Group
hussian_2020_fig9c_sd <- tapply(hussian_2020_fig9c$value, hussian_2020_fig9c$group, sd, na.rm = TRUE)

# Calculate standard error for each variable in group
hussian_2020_fig9c_se <- tapply(hussian_2020_fig9c$value, hussian_2020_fig9c$group, function(x) sd(x) / sqrt(length(x)))

hussian_2020_fig9c_sample_size <- tapply(hussian_2020_fig9c$value, hussian_2020_fig9c$group, length)

# Combine the results into a data frame
hussian_2020_fig9c_processed <- data.frame(Group= names(hussian_2020_fig9c_mean),
                                           Mean = hussian_2020_fig9c_mean,
                                           SD = hussian_2020_fig9c_sd,
                                           SE = hussian_2020_fig9c_se,
                                           Sample = hussian_2020_fig9c_sample_size)

# write.csv(hussian_2020_fig9c_processed, file.path(here("data_extraction", "data_extraction_figures"), "hussian_2020_fig9c_processed.csv"), row.names = FALSE)

```

Figure 9d extraction
```{r}
# Load the CSV file
hussian_2020_fig9d <- read_csv(here("data_extraction", "data_extraction_figures", "hussian_2020_fig9d_raw.csv"))

# Calculate mean for each variable in Group
hussian_2020_fig9d_mean <- tapply(hussian_2020_fig9d$value, hussian_2020_fig9d$group, mean, na.rm = TRUE)

# Calculate standard deviation for each variable in Group
hussian_2020_fig9d_sd <- tapply(hussian_2020_fig9d$value, hussian_2020_fig9d$group, sd, na.rm = TRUE)

# Calculate standard error for each variable in group
hussian_2020_fig9d_se <- tapply(hussian_2020_fig9d$value, hussian_2020_fig9d$group, function(x) sd(x) / sqrt(length(x)))

hussian_2020_fig9d_sample_size <- tapply(hussian_2020_fig9d$value, hussian_2020_fig9d$group, length)

# Combine the results into a data frame
hussian_2020_fig9d_processed <- data.frame(Group= names(hussian_2020_fig9d_mean),
                                           Mean = hussian_2020_fig9d_mean,
                                           SD = hussian_2020_fig9d_sd,
                                           SE = hussian_2020_fig9d_se,
                                           Sample = hussian_2020_fig9d_sample_size)

# write.csv(hussian_2020_fig9d_processed, file.path(here("data_extraction", "data_extraction_figures"), "hussian_2020_fig9d_processed.csv"), row.names = FALSE)

```

Figure 9e extraction
```{r}
# Load the CSV file
hussian_2020_fig9e <- read_csv(here("data_extraction", "data_extraction_figures", "hussian_2020_fig9e_raw.csv"))

# Calculate mean for each variable in Group
hussian_2020_fig9e_mean <- tapply(hussian_2020_fig9e$value, hussian_2020_fig9e$group, mean, na.rm = TRUE)

# Calculate standard deviation for each variable in Group
hussian_2020_fig9e_sd <- tapply(hussian_2020_fig9e$value, hussian_2020_fig9e$group, sd, na.rm = TRUE)

# Calculate standard error for each variable in group
hussian_2020_fig9e_se <- tapply(hussian_2020_fig9e$value, hussian_2020_fig9e$group, function(x) sd(x) / sqrt(length(x)))

hussian_2020_fig9e_sample_size <- tapply(hussian_2020_fig9e$value, hussian_2020_fig9e$group, length)

# Combine the results into a data frame
hussian_2020_fig9e_processed <- data.frame(Group= names(hussian_2020_fig9e_mean),
                                           Mean = hussian_2020_fig9e_mean,
                                           SD = hussian_2020_fig9e_sd,
                                           SE = hussian_2020_fig9e_se,
                                           Sample = hussian_2020_fig9e_sample_size)

# write.csv(hussian_2020_fig9e_processed, file.path(here("data_extraction", "data_extraction_figures"), "hussian_2020_fig9e_processed.csv"), row.names = FALSE)

```

Figure 9f extraction
```{r}
# Load the CSV file
hussian_2020_fig9f <- read_csv(here("data_extraction", "data_extraction_figures", "hussian_2020_fig9f_raw.csv"))

# Calculate mean for each variable in Group
hussian_2020_fig9f_mean <- tapply(hussian_2020_fig9f$value, hussian_2020_fig9f$group, mean, na.rm = TRUE)

# Calculate standard deviation for each variable in Group
hussian_2020_fig9f_sd <- tapply(hussian_2020_fig9f$value, hussian_2020_fig9f$group, sd, na.rm = TRUE)

# Calculate standard error for each variable in group
hussian_2020_fig9f_se <- tapply(hussian_2020_fig9f$value, hussian_2020_fig9f$group, function(x) sd(x) / sqrt(length(x)))

hussian_2020_fig9f_sample_size <- tapply(hussian_2020_fig9f$value, hussian_2020_fig9f$group, length)

# Combine the results into a data frame
hussian_2020_fig9f_processed <- data.frame(Group= names(hussian_2020_fig9f_mean),
                                           Mean = hussian_2020_fig9f_mean,
                                           SD = hussian_2020_fig9f_sd,
                                           SE = hussian_2020_fig9f_se,
                                           Sample = hussian_2020_fig9f_sample_size)

# write.csv(hussian_2020_fig9f_processed, file.path(here("data_extraction", "data_extraction_figures"), "hussian_2020_fig9f_processed.csv"), row.names = FALSE)

```





Collective behaviour figures
```{r}
hussian







hussian_2020_collective_behaviour_raw <- read.csv(here("data_extraction", "data_extraction_figures", "hussian_2020_collective_behaviour_raw.csv"))

hussian_2020_collective_behaviour_processed <- hussian_2020_collective_behaviour_raw %>% 
 mutate(mean_n = n_fish / n_shoal,
         design_effect = 1 + (mean_n - 1) * 0.5,
         n_effective = n_fish / design_effect,
         sd_shoal = se * sqrt(n_shoal),
         sd_fish = se * sqrt(n_fish))


# write.csv(hussian_2020_collective_behaviour_processed, file.path(here("data_extraction", "data_extraction_figures"), "hussian_2020_collective_behaviour_processed.csv"), row.names = FALSE)
```

# **Ibrahim et al., 2023**
DOI: 10.1016/j.aquatox.2023.106630
Table 1 extraction
```{r}
ibrahim_2023_raw <- read_csv(here("data_extraction", "data_extraction_figures", "ibrahim_2023_table1_raw.csv"))

ibrahim_2023_processed <- ibrahim_2023_raw %>%
  mutate(sd = se * sqrt(n))

# write.csv(ibrahim_2023_processed, file.path(here("data_extraction", "data_extraction_figures"), "ibrahim_2023_processed.csv"), row.names = FALSE)

```

# **Khalil et al., 2013**
DOI: 10.1016/j.chemosphere.2013.02.042
Collective behaviour figures
```{r}
khalil_2013_collective_behaviour_raw <- read_csv(here("data_extraction", "data_extraction_figures", "khalil_2013_collective_behaviour_raw.csv"))

khalil_2013_collective_behaviour_processed <- khalil_2013_collective_behaviour_raw %>%
  mutate(mean_n = n_fish / n_shoal,
         design_effect = 1 + (mean_n - 1) * 0.5,
         n_effective = n_fish / design_effect,
         sd_shoal = se * sqrt(n_shoal),
         sd_fish = se * sqrt(n_fish))

# write.csv(khalil_2013_collective_behaviour_processed, file.path(here("data_extraction", "data_extraction_figures"), "khalil_2013_collective_behaviour_processed.csv"), row.names = FALSE)

```

# **Khalil et al., 2017**
DOI: 10.1016/j.ecoenv.2017.07.007
Collective behaviour figures
```{r}
khalil_2017_collective_behaviour_raw <- read_csv(here("data_extraction", "data_extraction_figures", "khalil_2017_collective_behaviour_raw.csv"))

khalil_2017_collective_behaviour_processed <- khalil_2017_collective_behaviour_raw %>%
  mutate(mean_n = n_fish / n_shoal,
         design_effect = 1 + (mean_n - 1) * 0.5,
         n_effective = n_fish / design_effect,
         sd_shoal = se * sqrt(n_shoal),
         sd_fish = se * sqrt(n_fish))

# write.csv(khalil_2017_collective_behaviour_processed, file.path(here("data_extraction", "data_extraction_figures"), "khalil_2017_collective_behaviour_processed.csv"), row.names = FALSE)

```

# **Lei et al., 2022**
DOI: 10.1016/j.scitotenv.2022.153623
Collective behaviour figures
```{r}
lei_2022_collective_behaviour_raw <- read_csv(here("data_extraction", "data_extraction_figures", "lei_2022_collective_behaviour_raw.csv"))

lei_2022_collective_behaviour_processed <- lei_2022_collective_behaviour_raw %>%
  mutate(mean_n = n_fish / n_shoal,
         design_effect = 1 + (mean_n - 1) * 0.5,
         n_effective = n_fish / design_effect,
         sd_shoal = se * sqrt(n_shoal),
         sd_fish = se * sqrt(n_fish))

# write.csv(lei_2022_collective_behaviour_processed, file.path(here("data_extraction", "data_extraction_figures"), "lei_2022_collective_behaviour_processed.csv"), row.names = FALSE)

```

# **Leite et al., 2023**
DOI: 10.3390/fishes8090462
Collective behaviour figures
```{r}
leite_2023_collective_behaviour_raw <- read.csv(here("data_extraction", "data_extraction_figures", "leite_2023_collective_behaviour_raw.csv"))

leite_2023_collective_behaviour_processed <- leite_2023_collective_behaviour_raw %>%
  mutate(mean_n = n_fish / n_shoal,
         design_effect = 1 + (mean_n - 1) * 0.5,
         n_effective = n_fish / design_effect,
         sd_shoal = se * sqrt(n_shoal),
         sd_fish = se * sqrt(n_fish))

# write.csv(leite_2023_collective_behaviour_processed, file.path(here("data_extraction", "data_extraction_figures"), "leite_2023_collective_behaviour_processed.csv"), row.names = FALSE)

```

# **Lin et al., 2024**
DOI: 10.1016/j.ntt.2024.107323
Collective behaviour figures
```{r}
lin_2024_fig3d_collective_behaviour_raw <- read_csv(here("data_extraction", "data_extraction_figures", "lin_2024_fig3d_collective_behaviour_raw.csv"))

lin_2024_fig3d_collective_behaviour_processed <- lin_2024_fig3d_collective_behaviour_raw %>% 
    mutate(mean_n = n_fish / n_shoal,
         design_effect = 1 + (mean_n - 1) * 0.5,
         n_effective = n_fish / design_effect)

# write.csv(lin_2024_fig3d_collective_behaviour_processed, file.path(here("data_extraction", "data_extraction_figures"), "lin_2024_fig3d_collective_behaviour_processed.csv"), row.names = FALSE)

```

# **Liu et al., 2023**
DOI: 10.1016/j.aquatox.2023.106756
Figure 3 extraction
```{r}
liu_2023a_fig3_raw <- read_csv(here("data_extraction", "data_extraction_figures", "liu_2023a_fig3_raw.csv"))


liu_2023a_fig3_processed <-liu_2023a_fig3_raw %>%
  group_by(group_id) %>%
  mutate(diff_mean = mean(mean[zone == 2]) - mean(mean[zone == 1]))

# write.csv(liu_2023a_fig3_processed, file.path(here("data_extraction", "data_extraction_figures"), "liu_2023a_fig3_processed.csv"), row.names = FALSE)

```

# **Maclaren et al., 2023**
DOI: 10.3390/w15020307
Table 1 extraction
```{r}
maclaren_2023_table1_raw <- read_csv(here("data_extraction", "data_extraction_figures", "maclaren_2023_table1_raw.csv"))


maclaren_2023_table1_processed <- maclaren_2023_table1_raw %>%
  mutate(sd = se * sqrt(n))

# write.csv(maclaren_2023_table1_processed, file.path(here("data_extraction", "data_extraction_figures"), "maclaren_2023_table1_processed.csv"), row.names = FALSE)

```

# **Olsen et al., 2020**
DOI: 10.1007/s10695-020-00803-x
Figure 7c extraction
```{r}
olsen_2020 <- read_csv(here("data_extraction", "data_extraction_figures", "olsen_2020_fig1_raw.csv"))

# Calculate mean for each variable in Group
olsen2020_mean <- tapply(olsen_2020$time_with_female, olsen_2020$group, mean, na.rm = TRUE)

# Calculate standard deviation for each variable in Group
olsen2020_sd <- tapply(olsen_2020$time_with_female, olsen_2020$group, sd, na.rm = TRUE)

# Calculate standard error for each variable in Group
olsen_2020_se <- tapply(olsen_2020$time_with_female, olsen_2020$group, function(x) calculate_se(x) / sqrt(length(x)))
 
 
olsen_2020_sample_size <- tapply(olsen_2020$time_with_female, olsen_2020$group, length)

# Combine the results into a data frame
olsen_2020_processed<- data.frame(Group= names(olsen2020_mean),
                                       Mean = olsen2020_mean,
                             SD = olsen2020_sd,
                             SE = olsen_2020_se,
                             Sample = olsen_2020_sample_size)

# write.csv(olsen_2020_processed, file.path(here("data_extraction", "data_extraction_figures"), "olsen_2020_processed.csv"), row.names = FALSE)
```

# **Sanchez et al., 2021**
DOI: 10.1007/s11356-020-11958-8
Table 2 extraction
```{r}
sanchez_2021_table2_raw <- read_csv(here("data_extraction", "data_extraction_figures", "sanchez_2021_table2_raw.csv"))


sanchez_2021_table2_processed <- sanchez_2021_table2_raw %>%
  mutate(sd = se * sqrt(n))

# write.csv(sanchez_2021_table2_processed, file.path(here("data_extraction", "data_extraction_figures"), "sanchez_2021_table2_processed.csv"), row.names = FALSE)

```

# **Schmidel et al., 2024**
DOI: 10.1016/j.ntt.2014.05.006
Collective behaviour figures
```{r}
schmidel_2014_collective_behaviour_raw <- read_csv(here("data_extraction", "data_extraction_figures", "schmidel_2014_collective_behaviour_raw.csv"))

schmidel_2014_collective_behaviour_processed <- schmidel_2014_collective_behaviour_raw %>%
  mutate(mean_n = n_fish / n_shoal,
         design_effect = 1 + (mean_n - 1) * 0.5,
         n_effective = n_fish / design_effect,
         sd_shoal = se * sqrt(n_shoal),
         sd_fish = se * sqrt(n_fish))

# write.csv(schmidel_2014_collective_behaviour_processed, file.path(here("data_extraction", "data_extraction_figures"), "schmidel_2014_collective_behaviour_processed.csv"), row.names = FALSE)
```

# **Tamagno et al., 2023**
DOI:10.1016/j.neuro.2023.02.011
Collective behaviour figures
```{r}
tamagno_2023_collective_behaviour_raw <- read_csv(here("data_extraction", "data_extraction_figures", "tamagno_2023_collective_behaviour_raw.csv"))

tamagno_2023_collective_behaviour_processed <- tamagno_2023_collective_behaviour_raw %>%
  mutate(mean_n = n_fish / n_shoal,
         design_effect = 1 + (mean_n - 1) * 0.5,
         n_effective = n_fish / design_effect,
         sd_shoal = se * sqrt(n_shoal),
         sd_fish = se * sqrt(n_fish))

# write.csv(tamagno_2023_collective_behaviour_processed, file.path(here("data_extraction", "data_extraction_figures"), "tamagno_2023_collective_behaviour_processed.csv"), row.names = FALSE)


```

# **Yang et al., 2023**
DOI: 10.1016/j.scitotenv.2022.159883
Collective behaviour figures
```{r}
yang_2023_tables4_raw <- read_csv(here("data_extraction", "data_extraction_figures", "yang_2023_tables4_raw.csv"))

yang_2023_tables4_raw_with_SE <- yang_2023_tables4_raw %>% 
  mutate(SE = SD/sqrt(n))

# write.csv(yang_2023_tables4_raw_with_SE, file.path(here("data_extraction", "data_extraction_figures"), "yang_2023_tables4_raw_with_SE.csv"), row.names = FALSE)

yang_2023_tables4_collective_behaviour_raw <- yang_2023_tables4_raw_with_SE %>%
  filter(str_detect(measurement_level, "collective"))

# write.csv(yang_2023_tables4_collective_behaviour_raw, file.path(here("data_extraction", "data_extraction_figures"), "yang_2023_tables4_collective_behaviour_raw.csv"), row.names = FALSE)

yang_2023_tables4_collective_behaviour_processed <- yang_2023_tables4_collective_behaviour_raw %>%
  mutate(mean_n = n_fish / n_shoal,
         design_effect = 1 + (mean_n - 1) * 0.5,
         n_effective = n_fish / design_effect,
         sd_shoal = SE * sqrt(n_shoal),
         sd_fish = SE * sqrt(n_fish))

# write.csv(yang_2023_tables4_collective_behaviour_processed, file.path(here("data_extraction", "data_extraction_figures"), "yang_2023_tables4_collective_behaviour_processed.csv"), row.names = FALSE)

```

# **Zhou et al., 2021**
DOI: 10.1016/j.aquatox.2021.105917
Collective behaviour figures
```{r}
zhou_2021_collective_behaviour_raw <- read_csv(here("data_extraction", "data_extraction_figures", "zhou_2021_collective_behaviour_raw.csv"))

zhou_2021_collective_behaviour_processed <- zhou_2021_collective_behaviour_raw %>%
  mutate(mean_n = n_fish / n_shoal,
         design_effect = 1 + (mean_n - 1) * 0.5,
         n_effective = n_fish / design_effect,
         sd_shoal = se * sqrt(n_shoal),
         sd_fish = se * sqrt(n_fish))

# write.csv(zhou_2021_collective_behaviour_processed, file.path(here("data_extraction", "data_extraction_figures"), "zhou_2021_collective_behaviour_processed.csv"), row.names = FALSE)

```

